---
title: "Graph Function for univariate and bivariate analysis"
Created By : Kunal Bharadwaj(D19016), Veera Vignesh(D19036)
---

## Graph Function:

The purpose of this fuction is to automate the process of exploratory data analysis and generate univariate and bivariate graphs for the metrics.

## Output of the function:

1) Univariate graphs: 

Numerical Variables-Histogram and Box plot
Categorical variables-Pie Chart and Bar plot

2) Bivariate graphs:

Numerical vs Numerical - Scatter plot
Categorical vs Numerical - Box plot

3) Correlation matrix

## Code:


```{r graph}
#Function definition
graphs <- function(data,var=0,folder = getwd())
{
  library(corrplot)
  library(tidyverse)
  
  #Checking whether the data is passed as dataframe or else we stop the function execution and display a message to the user
  if(!is.data.frame(data))
    stop("The given object is not a data frame")
  
  #If no var is specified we take all the columns of the data
  if (var == 0)
    var = 1:ncol(data)
  
  #if the folder specified is not present we are setting it to the current directory
  if (!file.exists(folder)){
    print(paste('The path does not exist. Plots will be saved in working directory:' , getwd()))
    folder = getwd()
  }
  
  #Univariate analysis
  
  #Looping over the var
  
  for(i in var)
  {
    if(is.numeric(data[,i]))
    {
      data_level = length(levels(factor(data[,i])))
      if(data_level > 10){
        png(filename = paste(folder,paste('/',names(data)[i], ".png", sep=""),sep = ''))
        
        par(mfrow=c(2,1))
        #Box Plot
        boxplot(data[,i], main = paste("Boxplot of", names(data)[i]),
                ylab = names(data)[i], col = "maroon", border = "grey5",
                horizontal = T)
        
        # Histogram
        
        hist(data[,i], main = paste("Histogram of", names(data)[i]),
             xlab = names(data)[i], ylab = "Frequency", col = "lightgreen", border=F)
        dev.off()
      }
      else{
        png(filename = paste(folder,paste('/',names(data)[i], ".png", sep=""),sep = ''))
        par(mfrow=c(2,1))
        
        # Pie Chart
        pie(table(data[,i]), main = paste("Pie Chart of", names(data)[i]),
            col = rainbow(length((table(data[,i])))),radius = 1
        )
        
        # Bar Plot
        
        barplot(table(data[,i]), main = paste("Barplot of", names(data)[i]),
                xlab = names(data)[i], ylab = "Frequency", col = "lightgreen")
        
        dev.off()
      }
      
    }
    
  }
  
  #Bivariate analysis
  
  #Categorizing in numerical and categorical
  num_data<-data %>% select_if(is.numeric)
  cat_data<-data %>% select_if(is.factor)
  
  var1=1:(ncol(num_data)-1)
  var2=2:(ncol(num_data))
  for(i in var1)
  {
    for (j in var2)
    {
  #Scatter plot
      png(filename = paste(folder,paste('/',paste(names(num_data[i]),"vs",names(num_data[j])), ".png", sep=""),sep = ''))
      plot(num_data[,i], num_data[,j], main = paste(names(num_data[i]),"vs",names(num_data[j])),
           xlab = names(num_data[i]), ylab = names(num_data[j]),
           pch = 19, frame = FALSE,col=rgb((runif(1, min=0, max=1)),(runif(1, min=0, max=1)),(runif(1, min=0, max=1))))
      dev.off()
    }
  }
  
  if (dim(cat_data)[2]>0) {
    cat_var=1:(ncol(cat_data))
    num_var=1:(ncol(num_data))
    for(i in cat_var)
    {
      for (j in num_var)
      {
    #Box plot for groups
        png(filename = paste(folder,paste('/',paste(names(cat_data[i]),"vs",names(num_data[j])), ".png", sep=""),sep = ''))
        plot(cat_data[,i], num_data[,j], main = paste(names(cat_data[i]),"vs",names(num_data[j])),
             xlab = names(cat_data[i]), ylab = names(num_data[j]),
             pch = 19, frame = FALSE,col=rgb((runif(1, min=0, max=1)),(runif(1, min=0, max=1)),(runif(1, min=0, max=1))))
        dev.off()
      }
    }
    
  }
  
  
  
  # Correlation Matrix Heatmap
  png(filename = paste(folder,paste('/',"Correlation_plot", ".png", sep=""),sep = ''))
  corrplot(cor(num_data), method="color",
           diag=FALSE, # tl.pos="d",
           type="upper", order="hclust",
           title = 'Correlation plot of Data',
           addCoef.col = "black",
           mar=c(0,0,1,0)
  )
  dev.off()
  print(paste("the plots are generated:",folder))
}
```

## loading the data
```{r}

data=read.csv("C:/Users/kunal/Desktop/Praxis/R/cars.csv")
head(data)

```

## Calling the graph function
```{r}
graphs(data,folder="C:/Users/kunal/Desktop/Praxis/R/R assignment/images")
```

