---
title: "statistical test"
Created By : Kunal Bharadwaj(D19016)
---

## Statistical testing:

The purpose of this fuction is to automate the t-test and chi square test on the given dataset for the target variable.

## Input:

The input required for the function is the dataset on which the statistical testing needs to be performed
and the target variable.

## process:

The stat_test fuction checks the type of the variable of the dataset and performs the following test:

a) chi-square test for categorical variables
b) t-test for categorical variables

append the p-value for each variable in a list and give the output

## code:
```{r stat_test}
stat_test<-function(data,target_var)
{
  #check if the target is binary or not
  if (length(unique(data[,target_var])) == 2){
    #check if the data is a dataframe or not
    if(is.data.frame(data)){
      name = colnames(data)
      
      #check if the target is available in the data
      if (target_var %in% name){
        x<-data[colnames(data)!=target_var]
        
        p_value=c()
        
        
        var= 1:ncol(data)
        
        
        for(i in var){
          # check if the variable is categorical or the values are less than 10
          if (class(i)=="factor" | ((length(unique(data[,i])))<10 )) 
          {
          #perform chi-square test
            c_test=suppressWarnings(chisq.test(x = data[,i],y = data[,2]))
            chisq_test=c_test[3]
          #store the p-value in the list  
            p_value <- c(p_value,colnames(data[i]), chisq_test)
          }
            
          else{
          #if variable is numerical, perform t-test   
            t_t=t.test(data[,i]~data[,target_var])
            t_test=t_t[3]
            #store the p-value in the list
            p_value <- c(p_value,colnames(data[i]), t_test)
            
          }
         
        }
      }
      else{
        print('Error! variable is not in dataframe')
      }

    }
    else{
      print('Error! Not a data frame!')
    }
  }
  else{
    print('Error! The target variable is not binary!')
  }
  return(p_value)
}
```


## loading the data

```{r}
att=read.csv("attrition.csv")
head(att)
```

## applying stat_test fuction and retrieving p-values for all the variables

```{r}
stat_test(att,"Attrition")
```

```{r}
#writing the output in text file
capture.output(stat_test(att,"Attrition"), file = "p_value.txt")
```

